### 2014-05-21 acks.tex
Fix spelling in acks

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgements}%

@@

To my labmates and ninth floor coinhabitants---Katrina LaCurts, Raluca
Ada Popa, Shuo Deng, Lenin Ravindranath, Ravi Netravali, Peter
Iannucci, Tiffany Chen, Amy Ousterhout, Jonathan Perry, Neha Narula,
Austin Clements, Emily Stark, Cody Cutler, Eugene Wu, Dan Ports, Silas
Boyd-Wickizer, and Sheila Marian---thank you for your companionship
and our time together.

>>>>

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}%

@@

To my labmates and ninth floor cohabitants---Katrina LaCurts, Raluca
Ada Popa, Shuo Deng, Lenin Ravindranath, Ravi Netravali, Peter
Iannucci, Tiffany Chen, Amy Ousterhout, Jonathan Perry, Neha Narula,
Austin Clements, Emily Stark, Cody Cutler, Eugene Wu, Dan Ports, Silas
Boyd-Wickizer, and Sheila Marian---thank you for your companionship
and our time together.
